---
title: "Adding new decks"
author: "Corson N. Areshenkoff"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding new decks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Decks are stored as `.rds` files in `inst/extdata/decks`; all with the 
standard naming format `deck_KEYWORD.rds`. Internally, when a deck is identified
by name (e.g. `bechara`), iowa searches for the filename using

```{r,eval=FALSE}
system.file(paste0('extdata/decks/deck_', deck, '.rds'), package = "iowa")
```

And so as long as the deck is given a unique identifier, is named appropriately,
and is placed in the appropriate directory, it should be available to all
functions within the package (e.g. `simulateIGT()`) when the package is recompiled.

Note that this may be convenient if an alternative deck structure is used frequently,
but all relevant functions also accept custom deck structures as list objects 
(see the relevant article).
