---
title: "Deck structure"
author: "Corson N. Areshenkoff"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Deck structure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(iowa)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

A *deck structure* -- for the purposes of the **iowa** package -- is a named list of matrices,
containing the gains and losses for each deck. The list contains two fields: `win`
and `loss`, each of which is an $n \times k$ matrix or data frame, where each column
is a deck, and each row is a trial. In cases where the task produces only a net outcome,
this should be stored in the `win` slot, and the `loss` slot should be set to a
matrix of zeros. In cases where both a gain and a loss are presented, losses
stored in `loss` should be stored as positive values, as these values are *subtracted*
internally when computing net outcomes.

**iowa** includes several common deck structures, which can be loaded directly
using the `importDeck()` function, or can be identified by keyword in other package
functions. The following decks are included by default:

- `bechara`: The classic deck structure introduced by Bechara et al. (1994). In
the original publication, each deck contains only 40 cards. Here, the decks
contain 100 cards, consisting of 2.5 copies of the original decks. Two decks 
(A and B) have negative expected value, while the remaining (C and D) have 
positive expected value. Further, decks B and D have a high reward frequency,
with relatively infrequent losses.
- `becharavar`: A variant of `bechara` in which the losses of deck C are fixed
at 50, whereas the original losses vary between 25, 50, and 75.
- `soochow`: An alternative deck structure used by Lin et al. (2009) which
balances the gain/loss frequencies of pairs of good/bad decks.

Any of these decks can be loaded by passing the deck name to `importDeck()`, e.g.

```{r}
deck <- importDeck('bechara')
print(head(deck$loss))
```

Further, in functions accepting deck input (such as `simulateIGT()`), users can
identify any of these decks by name, in addition to the option of providing
a list containing a custom deck.

### References

Bechara, A., Damasio, A. R., Damasio, H., & Anderson, S. W. (1994). Insensitivity to future consequences following damage to human prefrontal cortex. Cognition, 50(1-3), 7-15.

Lin, C. H., Chiu, Y. C., & Huang, J. T. (2009). Gain-loss frequency and final outcome in the Soochow Gambling Task: A reassessment. Behavioral and Brain Functions, 5, 1-9.

